---
title: "Importance benchmark results"
format: 
  html_document:
    toc: true
    toc_float: true
---

```{r setup-appendix-01}
#| echo: false
knitr::opts_chunk$set(
	cache = FALSE,
	echo = FALSE,
	fig.height = 9,
	fig.width = 10,
	fig.align = "center"
)
source(here::here("R", "plotting.R"))
library(ggplot2)
library(data.table)
importances <- readRDS(here::here("results", "importance", "importances.rds"))
```

We present a complete set of the importance results in the form of boxplots split across FI method and learner type, separately for each dataset.
Table 1 lists all DGPs used in the importance benchmark.

```{r tab-importance-problems-supplement}
#| echo: false
library(kableExtra)
tibble::tribble(
	~DGP           , ~p , ~description                                          , ~model                                                                            ,
	"ewald"        ,  5 , "DGP used by Ewald et al. (2024)"                     , r"($Y = X_4 + X_5 + X_4 X_5 + \varepsilon$)"                                      ,
	"correlated"   ,  4 , "$X_1$ and $X_2$ correlated ($r = 0.25, 0.75$)"       , r"($Y = 2 X_1 + X_3 + \varepsilon$)"                                              ,
	"interactions" ,  5 , "$X_1$ and $X_2$ interact but have no direct effects" , r"($Y = 2 X_1 X_2 + X_3 + \varepsilon$)"                                          ,
	"friedman1"    , 10 , "Regression benchmark from mlbench"                   , r"($Y = 10 \sin(\pi X_1 X_2) + 20 (X_3 - 0.5)^2 + 10 X_4 + 5 X_5 + \varepsilon$)" ,
	"independent"  ,  5 , "Uncorrelated features with direct effects"           , r"($Y = 2 X_1 + X_2 + 0.5 X_3 + \varepsilon$)"                                    ,
	"confounded"   ,  4 , "Unobserved confounder $H$ with proxy"                , r"($Y = H + X_1 + \varepsilon$)"                                                  ,
	"mediated"     ,  4 , "Mediator masks exposure variable"                    , r"($Y = 1.5 \cdot \mathrm{mediator} + 0.5 \cdot \mathrm{direct} + \varepsilon$)"  ,
	"bike sharing" , 12 , "Real-world dataset from mlr3data"                    , "N/A"
) |>
	kbl(
		col.names = c("Dataset", "p", "Description", "Model"),
		caption = "DGPs used for comparison, alongside their number of features (p) and a brief description. Unless otherwise specified, features in simulated data were drawn from a univariate normal distribution and do not have an effect on the target.",
		escape = FALSE,
		booktabs = TRUE
	) |>
	kable_styling()
```

## Importance (scaled) {.tabset}

Importances are scaled to percentages such that 100 is the highest importance value assigned by the corresponding method on a dataset in a given replication.

### Confounded

```{r ap-plot-confounded}
#| fig.cap: Scaled feature importance scores for the Confounded task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "scaled",
	problem = "confounded",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

### Correlated

```{r ap-plot-correlated-25}
#| fig.cap: Scaled feature importance scores for the Correlated (r = 0.25) task by FI method and learner, colored by implementing package.
plot_importance(
	importances[correlation == 0.25],
	type = "scaled",
	problem = "correlated",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

```{r ap-plot-correlated-75}
#| fig.cap: Scaled feature importance scores for the Correlated (r = 0.75) task by FI method and learner, colored by implementing package.
plot_importance(
	importances[correlation == 0.75],
	type = "scaled",
	problem = "correlated",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```


### Ewald

```{r ap-plot-ewald}
#| fig.cap: Scaled feature importance scores for the Ewald task by FI method and learner, colored by implementing package.
#| #| fig.height: 10
#| fig.width: 10
plot_importance(
	importances,
	type = "scaled",
	problem = "ewald",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```


### Friedman1

```{r ap-plot-friedman1}
#| fig.cap: Scaled feature importance scores for the Friedman1 task by FI method and learner, colored by implementing package.
#| fig.height: 14
plot_importance(
	importances,
	type = "scaled",
	problem = "friedman1",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

### Independent

```{r ap-plot-independent}
#| fig.cap: Scaled feature importance scores for the Independent task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "scaled",
	problem = "independent",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

### Interactions

```{r ap-plot-interactions}
#| fig.cap: Scaled feature importance scores for the Interactions task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "scaled",
	problem = "interactions",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```


### Mediated

```{r ap-plot-mediated}
#| fig.cap: Scaled feature importance scores for the mediated task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "scaled",
	problem = "mediated",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

### Bike sharing

```{r ap-plot-bikesharing}
#| fig.height: 13
#| fig.cap: Scaled feature importance scores for the bike sharing task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "scaled",
	problem = "bike_sharing",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```


## Importance (ranks) {.tabset}

Importances are converted to ranks with 1 being the highest importance score.
Boxplots across ranks illustrate how consistent the rankings are.

### Confounded

```{r ap-plot-confounded-ranks}
#| fig.cap: Ranked feature importance scores for the Confounded task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "rank",
	problem = "confounded",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

### Correlated

```{r ap-plot-correlated-25-rank}
#| fig.cap: Ranked feature importance scores for the Correlated (r = 0.25) task by FI method and learner, colored by implementing package.
plot_importance(
	importances[correlation == 0.25],
	type = "rank",
	problem = "correlated",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

```{r ap-plot-correlated-75-rank}
#| fig.cap: Ranked feature importance scores for the Correlated (r = 0.75) task by FI method and learner, colored by implementing package.
plot_importance(
	importances[correlation == 0.75],
	type = "rank",
	problem = "correlated",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```


### Ewald

```{r ap-plot-ewald-rank}
#| fig.cap: Ranked feature importance scores for the Ewald task by FI method and learner, colored by implementing package.
#| #| fig.height: 10
#| fig.width: 10
plot_importance(
	importances,
	type = "rank",
	problem = "ewald",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```


### Friedman1

```{r ap-plot-friedman1-rank}
#| fig.cap: Ranked feature importance scores for the Friedman1 task by FI method and learner, colored by implementing package.
#| fig.height: 14
plot_importance(
	importances,
	type = "rank",
	problem = "friedman1",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

### Independent

```{r ap-plot-independent-rank}
#| fig.cap: Ranked feature importance scores for the Independent task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "rank",
	problem = "independent",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

### Interactions

```{r ap-plot-interactions-rank}
#| fig.cap: Ranked feature importance scores for the Interactions task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "rank",
	problem = "interactions",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```


### Mediated

```{r ap-plot-mediated-rank}
#| fig.cap: Ranked feature importance scores for the mediated task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "rank",
	problem = "mediated",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```

### Bike sharing

```{r ap-plot-bikesharing-rank}
#| fig.height: 13
#| fig.cap: Ranked feature importance scores for the bike sharing task by FI method and learner, colored by implementing package.
plot_importance(
	importances,
	type = "rank",
	problem = "bike_sharing",
	method = NULL,
	color = "package",
	facets = c("method", "learner_type"),
	ncol = 4,
	title = TRUE
)
```
